\bf Title

### 2023-10-10 article/paper_padic_spec.tex
Ajout notations + Serre dans la biblio.

@@

@@

>>>>

\usepackage{stmaryrd} %for double brackets

@@

%p-adic commands
\DeclareMathOperator{\val}{val}
\def\QQ{\ensuremath{\mathbb{Q}}}
\def\ZZ{\ensuremath{\mathbb{Z}}}
\newcommand{\OK}{\mathcal{O}_K}

@@

Throughout the paper, $K$ refers to a complete,
discrete valuation field, $\val : K \twoheadrightarrow \ZZ \cup \{+\infty\}$ to its valuation,
$\OK$ its ring of integers and $\pi$ a uniformizer.
For $k \in \N$, we write $O(\pi^k)$ for $\pi^k \OK.$
A typical example of $K$ as above is the field of $p$-adic numbers 
$\QQ_p$ (equipped with the $p$-adic valuation). For this example, we 
have $\OK = \ZZ_p$.
Another example is the field of Laurent series
$K=\QQ ((T))$ equiped with $T$-adic valuation.
In this case,  $\OK = \QQ \llbracket T \rrbracket$.
We refer to Serre's Local Fields \cite{Serre} for a
general introduction to such fields
and to Caruso's course on $p$-adic computations \cite{caruso_computations_2017}
for an introduction to effective computations
over them
